### 2020-08-18 manuscript/manuscript.rmd
more uniform scales on Extended Data Fig. 1

matrix_overlap_rectangles %>%
  ggplot( ) +
    scale_x_continuous(name = "Genes") +
    scale_y_continuous(name = "Species") +
    geom_rect( mapping = aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = MSA ), alpha = 0.5) +
    facet_grid( matrix_1 ~ matrix_2, scales = "free" ) +
    theme( axis.text.x = element_text(angle = 45, hjust = 1),
           strip.text.y = element_text(angle = 0),
           strip.text.x = element_text(angle = 60))

>>>>

matrix_overlap_rectangles %>%
  ggplot( ) +
    scale_x_continuous(name = "Genes") +
    scale_y_continuous(name = "Species") +
    geom_rect( mapping = aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = MSA ), alpha = 0.5) +
    facet_grid( matrix_1 ~ matrix_2) +
    theme( axis.text.x = element_text(angle = 45, hjust = 1),
           strip.text.y = element_text(angle = 0),
           strip.text.x = element_text(angle = 60))
